---
title: "Meta-Analysis of Single-Case Design Research: Application of Multilevel Modeling"
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    toc_float: true
    code_folding: hide
    self_contained: false
---

```{r setup, include = FALSE}
knitr::opts_chunk$set(
  cache = TRUE,
  message = FALSE, 
  warning = FALSE)
```

This webpage contains the coded dataset, outputs, and R codes used for the four-level multilevel modeling in Authors (2023). Data analysis scripts have been posted through an online data repository, accessible at <https://osf.io/8wbta/?view_only=31ca7d3193104652b39dbb4a516a5f00>.

```{r, echo = FALSE}
suppressPackageStartupMessages({
  library(magrittr)
  library(readr)
  library(kableExtra)
  library(fastDummies)
  library(imputeTS)
  library(DT)
  library(tidyr)
  library(dplyr)
  library(downloadthis)
  library(ggh4x)
  library(broom)
  library(gridExtra)
  library(SingleCaseES)
  library(nlme)
  library(clubSandwich)
  library(lmeInfo)
  library(msm)
})
```

# Preprocess Data 

```{r}
wp_data <- read.csv("data/wp_data.csv")

# Create dummy variables
wp_data_dummy <-
  wp_data %>% dummy_cols(select_columns = c('designType', 'phase', 'complexityMeasure'))
colnames(wp_data_dummy) <- sub(".*_", "", colnames(wp_data_dummy))
wp_data_dummy %<>% select(
  authorYear, study, designType, multiBase, multiProbe, cluster, case, phase, A, B, M, 
  session, outcome, complexityMeasure, singleType, mixedType, generalization
)

# Center times and create interaction terms
wp_data_mixed <- wp_data_dummy %>%
  group_by(study, cluster, case) %>%
  mutate(
    min_A = ifelse(A == 1, min(session[A == 1]), NA),
    min_B = ifelse(B == 1, min(session[B == 1]), NA),
    min_M = ifelse(M == 1, min(session[M == 1]), NA)
  )

wp_data_mlm <- wp_data_mixed %>%
  group_by(study, cluster, case) %>%
  mutate(level_AB = as.integer(I(session >= first(na.omit(
    min_B
  ))))) %>%
  mutate(level_BM = as.integer(I(session >= first(na.omit(
    min_M
  ))))) %>%
  mutate(time_A = session - first(na.omit(min_A))) %>%
  mutate(time_B = session - first(na.omit(min_B))) %>%
  mutate(time_M = session - first(na.omit(min_M))) %>%
  mutate(trend_AB = time_B * level_AB) %>%
  mutate(trend_BM = time_M * level_BM) %>%
  select(-min_A,-min_B,-min_M)

wp_data_mlm <- na_replace(wp_data_mlm, 0)

wp_data_mlm_kb <- wp_data_mlm %>%
  kbl(align = "c") %>%
  kable_styling(
    bootstrap_options = c("striped", "hover", "condensed"),
    full_width = T,
    font_size = 12,
    fixed_thead = T
  ) %>%
  scroll_box(height = "400px")

wp_data_mlm %>%
  download_this(
    output_name = "Authors (2023) Dataset",
    output_extension = ".xlsx",
    button_label = "Download",
    button_type = "default",
    has_icon = TRUE,
    icon = "fa fa-save",
    class = "buttom_small"
  )
```

```{r, echo = FALSE}
load("data/wp_data.RData")

wp_data_mlm_kb
```

# Model Specification {.tabset}

## Model.1 

#### **Null model** 

```{r, eval = FALSE, class.source = 'fold-show'}
Model.1 <- lme(
  outcome ~ 1, # Overall intercept (mean)
  data = wp_data_mlm,
  method = "REML",
  random = ~ 1 | study/cluster/case,
  control = list(
    maxIter = 100, # 100 iterations for the lme optimization algorithm
    msMaxIter = 100, # 100 iterations for the optimization step inside the lme optimization
    tolerance = 1e-3, # Tolerance for the convergence criterion
    opt = "optim",
    optimMethod = "BFGS" # Optimization algorithm for unconstrained nonlinear problems
  )
)
```

#### **Cluster-robust variance estimation**

```{r}
options(width = 100)
Model.1.vcov <- vcovCR(Model.1, type = "CR2") # Calculate variance-covariance matrix
Model.1.crve <-
  coef_test(Model.1, vcov = Model.1.vcov , test = "Satterthwaite") # Test regression coefficients 

Model.1.crve$sig <-
  case_when(
    is.na(Model.1.crve$p_Satt) ~ "",
    Model.1.crve$p_Satt < 0.001 ~ "***",
    Model.1.crve$p_Satt < 0.01 ~ "**",
    Model.1.crve$p_Satt < 0.05 ~ "*",
    TRUE ~ ""
  )

# Calculate standardized mean difference (d)
Model.1.d <- Model.1.crve %>%
  mutate(d = 2*abs(tstat)/sqrt(df_Satt)) %>%
  select(d)

Model.1.crve.mixed <- cbind(Model.1.crve, Model.1.d) %>%
  mutate_if(is.numeric, ~ round(., 3)) %>% tibble() %>%
  rename(
    Estimate = beta,
    "t-stat" = tstat,
    "d.f. (Satt)" = df_Satt,
    "p-val (Satt)" = p_Satt
  )

Model.1.crve.mixed %>%
  datatable(options = list(
    initComplete = JS(
      "
      function(settings, json) {
        $(this.api().table().header()).css({
          'font-family': 'Arial, sans-serif',
          'font-size': '13px',
        });
      }
    "
    )
  )) %>%
  formatStyle(columns = colnames(.$x$data), `font-size` = "13px")
```

#### **Variance components**

```{r, comment = NA, class.source = 'fold-show'}
# Obtain 95% confidence intervals for estimates
intervals(Model.1, which = "var-cov")
```

```{r, comment = NA, class.source = 'fold-show'}
# Obtain variance components
VarCorr(Model.1) 
```

```{r,comment = NA, class.source = 'fold-show'}
# Estimate the standard errors of variances
sqrt(diag(varcomp_vcov(Model.1))) 
```

#### **Intraclass correlation (ICC)** 

**Level 4 (study)**

```{r, comment = NA}
total_var <- as.numeric(VarCorr(Model.1)[[2]]) +
  as.numeric(VarCorr(Model.1)[[4]]) +
  as.numeric(VarCorr(Model.1)[[6]]) +
  as.numeric(VarCorr(Model.1)[[7]])

ICC.L4 = as.numeric(VarCorr(Model.1)[[2]]) / total_var
ICC.L4
```

**Level 3 (cluster)**

```{r, comment = NA}
ICC.L3 = (as.numeric(VarCorr(Model.1)[[4]])) / total_var
ICC.L3
```

**Level 2 (case)** 

```{r, comment = NA}
ICC.L2 = (as.numeric(VarCorr(Model.1)[[6]])) / total_var
format(ICC.L2, scientific = FALSE)
```

#### **Autocorrelation**

```{r, fig.align = 'center', fig.width = 7, fig.height = 4}
acf_Model.1 <- ACF(Model.1, maxLag = 14) # maximum number of time lag is 14
acf_Model.1.plot <- plot(acf_Model.1, alpha = .05)
acf_Model.1.value <- tidy(acf_Model.1$ACF) %>%
  mutate(acf = round(x, 2)) %>%
  select(acf)
acf_Model.1.tb <-
  tableGrob(acf_Model.1.value[1:10,],
            rows = NULL,
            theme = ttheme_default(base_size = 10))
grid.arrange(acf_Model.1.plot,
             acf_Model.1.tb,
             nrow = 1,
             widths = c(0.85, 0.15))
```

## Model.2 

#### **AR(1) correlation structure and homogeneous level-1 variances**

```{r, eval = FALSE, class.source = 'fold-show'}
Model.2 <- lme(
  outcome ~
    time_A + level_AB + trend_AB + level_BM + trend_BM, # piecewise growth model
  data = wp_data_mlm,
  method = "REML",
  random = ~ level_AB | study/cluster/case,
  correlation = corAR1(value = 0.3, form = ~ session | # AR(1) correlation structure
                         study/cluster/case),
  control = list(
    maxIter = 100, # 100 iterations for the lme optimization algorithm
    msMaxIter = 100, # 100 iterations for the optimization step inside the lme optimization
    tolerance = 1e-3, # Tolerance for the convergence criterion
    opt = "optim",
    optimMethod = "BFGS" # Optimization algorithm for unconstrained nonlinear problems
  )
)
```

#### **Cluster-robust variance estimation**

```{r}
options(width = 100)
Model.2.vcov <- vcovCR(Model.2, type = "CR2") # Calculate variance-covariance matrix
Model.2.crve <-
  coef_test(Model.2, vcov = Model.2.vcov , test = "Satterthwaite") # Test regression coefficients 

Model.2.crve$sig <-
  case_when(
    is.na(Model.2.crve$p_Satt) ~ "",
    Model.2.crve$p_Satt < 0.001 ~ "***",
    Model.2.crve$p_Satt < 0.01 ~ "**",
    Model.2.crve$p_Satt < 0.05 ~ "*",
    TRUE ~ ""
  )

# Calculate standardized mean difference (d)
Model.2.d <- Model.2.crve %>%
  mutate(d = 2*abs(tstat)/sqrt(df_Satt)) %>%
  select(d)

Model.2.crve.mixed <- cbind(Model.2.crve, Model.2.d) %>%
  mutate_if(is.numeric, ~ round(., 3)) %>% tibble() %>%
  rename(
    Estimate = beta,
    "t-stat" = tstat,
    "d.f. (Satt)" = df_Satt,
    "p-val (Satt)" = p_Satt
  )

Model.2.crve.mixed %>%
  datatable(options = list(
    initComplete = JS(
      "
      function(settings, json) {
        $(this.api().table().header()).css({
          'font-family': 'Arial, sans-serif',
          'font-size': '13px',
        });
      }
    "
    )
  )) %>%
  formatStyle(columns = colnames(.$x$data), `font-size` = "13px")
```

#### **Variance components**

```{r, comment = NA, class.source = 'fold-show'}
# Obtain 95% confidence intervals for estimates
intervals(Model.2, which = "var-cov")
```

```{r, comment = NA, class.source = 'fold-show'}
# Obtain variance components
VarCorr(Model.2) 
```

```{r,comment = NA, class.source = 'fold-show'}
# Estimate the standard errors of variances
sqrt(diag(varcomp_vcov(Model.2)))
```

#### **Autocorrelation**

```{r, fig.align = 'center', fig.width = 7, fig.height = 4}
acf_Model.2 <- ACF(Model.2, maxLag = 14) 
acf_Model.2.plot <- plot(acf_Model.2, alpha = .05)
acf_Model.2.value <- tidy(acf_Model.2$ACF) %>%
  mutate(acf = round(x, 2)) %>%
  select(acf)
acf_Model.2.tb <-
  tableGrob(acf_Model.2.value[1:10,],
            rows = NULL,
            theme = ttheme_default(base_size = 10))
grid.arrange(acf_Model.2.plot,
             acf_Model.2.tb,
             nrow = 1,
             widths = c(0.85, 0.15))
```

## Model 3
 
#### **AR(1) correlation structure and heterogenous residual variances** 

```{r, eval = FALSE, class.source = 'fold-show'}
Model.3 <- lme(
  outcome ~
    time_A + level_AB + trend_AB + level_BM + trend_BM, # piecewise growth model
  data = wp_data_mlm,
  method = "REML",
  random = ~ level_AB | study/cluster/case,
  correlation = corAR1(value = 0.3, form = ~ session | # AR(1) correlation structure
                         study/cluster/case),
  weights = varIdent(form = ~ 1 | # heterogenous residual variances across phases
                       phase),
  control = list(
    maxIter = 100, # 100 iterations for the lme optimization algorithm
    msMaxIter = 100, # 100 iterations for the optimization step inside the lme optimization
    tolerance = 1e-3, # Tolerance for the convergence criterion
    opt = "optim",
    optimMethod = "BFGS" # Optimization algorithm for unconstrained nonlinear problems
  )
)
```

#### **Cluster-robust variance estimation**

```{r}
options(width = 100)
Model.3.vcov <- vcovCR(Model.3, type = "CR2") # Calculate variance-covariance matrix
Model.3.crve <-
  coef_test(Model.3, vcov = Model.3.vcov , test = "Satterthwaite") # Test regression coefficients 

Model.3.crve$sig <-
  case_when(
    is.na(Model.3.crve$p_Satt) ~ "",
    Model.3.crve$p_Satt < 0.001 ~ "***",
    Model.3.crve$p_Satt < 0.01 ~ "**",
    Model.3.crve$p_Satt < 0.05 ~ "*",
    TRUE ~ ""
  )

# Calculate standardized mean difference (d)
Model.3.d <- Model.3.crve %>%
  mutate(d = 2*abs(tstat)/sqrt(df_Satt)) %>%
  select(d)

Model.3.crve.mixed <- cbind(Model.3.crve, Model.3.d) %>%
  mutate_if(is.numeric, ~ round(., 3)) %>% tibble() %>%
  rename(
    Estimate = beta,
    "t-stat" = tstat,
    "d.f. (Satt)" = df_Satt,
    "p-val (Satt)" = p_Satt
  )

Model.3.crve.mixed %>%
  datatable(options = list(
    initComplete = JS(
      "
      function(settings, json) {
        $(this.api().table().header()).css({
          'font-family': 'Arial, sans-serif',
          'font-size': '13px',
        });
      }
    "
    )
  )) %>%
  formatStyle(columns = colnames(.$x$data), `font-size` = "13px")
```

#### **Variance components**

```{r, comment = NA, class.source = 'fold-show'}
# Obtain 95% confidence intervals for estimates
intervals(Model.3, which = "var-cov")
```

```{r, comment = NA, class.source = 'fold-show'}
# Obtain variance components
VarCorr(Model.3) 
```

```{r, comment = NA, class.source = 'fold-show'}
# Extract heterogeneous residual variances
var_Model.3 <- extract_varcomp(Model.3, separate_variances = T)
var_Model.3 <- var_Model.3$sigma_sq %>% as.data.frame()
colnames(var_Model.3) <- NULL
var_Model.3 
```

```{r,comment = NA}
# Estimate the standard errors of variances
var.Model.3 <- Model.3$apVar
par.Model.3 <-
  attr(var.Model.3, "Pars") # logged standard deviations
par.Model.3[11] <- "0.1814115"
par.Model.3[12] <- "0.2695840"
par.Model.3 <- par.Model.3 %>% as.numeric()

se.vc.Model.3 <- c()
se.vc.Model.3[1] <-
  deltamethod (~ exp(x1)^2, par.Model.3, var.Model.3) # transform them to variances:
se.vc.Model.3[2] <-
  deltamethod (~ exp(x2)^2, par.Model.3, var.Model.3)
se.vc.Model.3[3] <-
  deltamethod (~ exp(x3)^2, par.Model.3, var.Model.3)
se.vc.Model.3[4] <-
  deltamethod (~ exp(x4)^2, par.Model.3, var.Model.3)
se.vc.Model.3[5] <-
  deltamethod (~ exp(x5)^2, par.Model.3, var.Model.3)
se.vc.Model.3[6] <-
  deltamethod (~ exp(x6)^2, par.Model.3, var.Model.3)
se.vc.Model.3[7] <-
  deltamethod (~ exp(x7)^2, par.Model.3, var.Model.3)
se.vc.Model.3[8] <-
  deltamethod (~ exp(x8)^2, par.Model.3, var.Model.3)
se.vc.Model.3[9] <-
  deltamethod (~ exp(x9)^2, par.Model.3, var.Model.3)
se.vc.Model.3[10] <-
  deltamethod (~ exp(x10)^2, par.Model.3, var.Model.3)
se.vc.Model.3[11] <-
  deltamethod (~ exp(x11)^2, par.Model.3, var.Model.3)
se.vc.Model.3[12] <-
  deltamethod (~ exp(x12)^2, par.Model.3, var.Model.3)
se.vc.Model.3[13] <-
  deltamethod (~ exp(x13)^2, par.Model.3, var.Model.3)

se.vc.Model.3.td <- data.frame(
  Names = c(
    "Tau.intercept.study",
    "Tau.level_AB.study",
    "Cov((intercept),level_AB).study",
    "Tau.intercept.cluster",
    "Tau.level_AB.cluster",
    "Cov((intercept),level_AB).cluster",
    "Tau.intercept.case",
    "Tau.level_AB.case",
    "Cov((intercept),level_AB).case",
    "CorStruct",
    "Sigma.sq(Intervention)",
    "Sigma.sq(Maintenance)",
    "Sigma.sq(Baseline)"
  ),
  Values = round(se.vc.Model.3, digits = 5)
)
rownames(se.vc.Model.3.td) <- NULL
colnames(se.vc.Model.3.td) <-
  c("Parameter Names", "Standard Errors")
print(se.vc.Model.3.td, row.names = FALSE)
```

#### **Autocorrelation**

```{r, fig.align = 'center', fig.width = 7, fig.height = 4}
acf_Model.3 <- ACF(Model.3, maxLag = 14) 
acf_Model.3.plot <- plot(acf_Model.3, alpha = .05)
acf_Model.3.value <- tidy(acf_Model.3$ACF) %>%
  mutate(acf = round(x, 2)) %>%
  select(acf)
acf_Model.3.tb <-
  tableGrob(acf_Model.3.value[1:10, ],
            rows = NULL,
            theme = ttheme_default(base_size = 10))
grid.arrange(acf_Model.3.plot,
             acf_Model.3.tb,
             nrow = 1,
             widths = c(0.85, 0.15))
```

#### **Likelihood ratio test for heterogeneous residual variances across phases**

```{r, comment = NA, class.source = 'fold-show'}
anova(Model.2, Model.3)
```


## Model.4

#### **Types of word problem measures as a moderator**

```{r, eval = FALSE, class.source = 'fold-show'}
Model.4 <- lme(
  outcome ~
    time_A + level_AB + trend_AB + level_BM + trend_BM + # piecewise growth model
    mixedType + time_A:mixedType + level_AB:mixedType + # Interactions with mixedTypes 
    trend_AB:mixedType + level_BM:mixedType + trend_BM:mixedType +
    generalization + time_A:generalization + level_AB:generalization + # Interactions with generalization
    trend_AB:generalization + level_BM:generalization + trend_BM:generalization,
  data = wp_data_mlm,
  method = "REML",
  random = ~ level_AB | study/cluster/case,
  correlation = corAR1(value = 0.2, form = ~ session | # AR(1) correlation structure
                         study/cluster/case),
  weights = varIdent(form = ~ 1 | phase), # heterogenous residual variances across phases
  control = list(
    maxIter = 100, # 100 iterations for the lme optimization algorithm
    msMaxIter = 100, # 100 iterations for the optimization step inside the lme optimization
    tolerance = 1e-3, # Tolerance for the convergence criterion
    opt = "optim",
    optimMethod = "BFGS" # Optimization algorithm for unconstrained nonlinear problems
  )
)
```

#### **Cluster-robust variance estimation**

```{r}
options(width = 100)
Model.4.vcov <- vcovCR(Model.4, type = "CR2")  # Calculate variance-covariance matrix
Model.4.crve <-
  coef_test(Model.4, vcov = Model.4.vcov, test = "Satterthwaite") # Test regression coefficients 

Model.4.crve$sig <-
  case_when(
    is.na(Model.4.crve$p_Satt) ~ "",
    Model.4.crve$p_Satt < 0.001 ~ "***",
    Model.4.crve$p_Satt < 0.01 ~ "**",
    Model.4.crve$p_Satt < 0.05 ~ "*",
    TRUE ~ ""
  )

# Calculate standardized mean difference (d)
Model.4.d <- Model.4.crve %>%
  mutate(d = 2*abs(tstat)/sqrt(df_Satt)) %>%
  select(d)

Model.4.crve.mixed <- cbind(Model.4.crve, Model.4.d) %>%
  mutate_if(is.numeric, ~ round(., 3)) %>% tibble() %>%
  rename(
    Estimate = beta,
    "t-stat" = tstat,
    "d.f. (Satt)" = df_Satt,
    "p-val (Satt)" = p_Satt
  )

Model.4.crve.mixed %>%
  datatable(options = list(
    initComplete = JS(
      "
      function(settings, json) {
        $(this.api().table().header()).css({
          'font-family': 'Arial, sans-serif',
          'font-size': '13px',
        });
      }
    "
    )
  )) %>%
  formatStyle(columns = colnames(.$x$data), `font-size` = "13px")
```

#### **Assess the significance of the model's coefficients**

```{r, comment = NA, class.source = 'fold-show'}
# Baseline level
Wald_test(Model.4,
          constraints = constrain_zero(c(
            "(Intercept)",
            "mixedType",
            "generalization"
          ),
          reg_ex = FALSE),
          vcov = Model.4.vcov)
```

```{r, comment = NA, class.source = 'fold-show'}
# Baseline trend
Wald_test(Model.4,
          constraints = constrain_zero("^time_A",
          reg_ex = TRUE),
          vcov = Model.4.vcov)
```

```{r, comment = NA, class.source = 'fold-show'}
# Change in level AB 
Wald_test(Model.4,
          constraints = constrain_zero("^level_AB",
          reg_ex = TRUE),
          vcov = Model.4.vcov)
```

```{r, comment = NA, class.source = 'fold-show'}
# Change in trend AB 
Wald_test(Model.4,
          constraints = constrain_zero("^trend_AB",
          reg_ex = TRUE),
          vcov = Model.4.vcov)
```

```{r, comment = NA, class.source = 'fold-show'}
# Change in level BM  
Wald_test(Model.4,
          constraints = constrain_zero("^level_BM",
          reg_ex = TRUE),
          vcov = Model.4.vcov)
```

```{r, comment = NA, class.source = 'fold-show'}
# Change in trend BM  
Wald_test(Model.4,
          constraints = constrain_zero("^trend_BM",
          reg_ex = TRUE),
          vcov = Model.4.vcov)
```

#### **Variance components**

```{r, comment = NA, class.source = 'fold-show'}
# Obtain 95% confidence intervals for estimates
intervals(Model.4, which = "var-cov")
```

```{r, comment = NA, class.source = 'fold-show'}
# Obtain variance components
VarCorr(Model.4) 
```

```{r, comment = NA, class.source = 'fold-show'}
# Extract heterogeneous residual variances
var_Model.4 <- extract_varcomp(Model.4, separate_variances = T)
var_Model.4 <- var_Model.4$sigma_sq %>% as.data.frame()
colnames(var_Model.4) <- NULL
var_Model.4 
```

```{r, comment = NA}
# Estimate the standard errors of variances
var.Model.4 <- Model.4$apVar
par.Model.4 <-
  attr(var.Model.4, "Pars") # logged standard deviations
par.Model.4[11] <- "0.09077629"
par.Model.4[12] <- "0.15454186"
par.Model.4 <- par.Model.4 %>% as.numeric()

se.vc.Model.4 <- c()
se.vc.Model.4[1] <-
  deltamethod (~ exp(x1)^2, par.Model.4, var.Model.4) # transform them to variances:
se.vc.Model.4[2] <-
  deltamethod (~ exp(x2)^2, par.Model.4, var.Model.4)
se.vc.Model.4[3] <-
  deltamethod (~ exp(x3)^2, par.Model.4, var.Model.4)
se.vc.Model.4[4] <-
  deltamethod (~ exp(x4)^2, par.Model.4, var.Model.4)
se.vc.Model.4[5] <-
  deltamethod (~ exp(x5)^2, par.Model.4, var.Model.4)
se.vc.Model.4[6] <-
  deltamethod (~ exp(x6)^2, par.Model.4, var.Model.4)
se.vc.Model.4[7] <-
  deltamethod (~ exp(x7)^2, par.Model.4, var.Model.4)
se.vc.Model.4[8] <-
  deltamethod (~ exp(x8)^2, par.Model.4, var.Model.4)
se.vc.Model.4[9] <-
  deltamethod (~ exp(x9)^2, par.Model.4, var.Model.4)
se.vc.Model.4[10] <-
  deltamethod (~ exp(x10)^2, par.Model.4, var.Model.4)
se.vc.Model.4[11] <-
  deltamethod (~ exp(x11)^2, par.Model.4, var.Model.4)
se.vc.Model.4[12] <-
  deltamethod (~ exp(x12)^2, par.Model.4, var.Model.4)
se.vc.Model.4[13] <-
  deltamethod (~ exp(x13)^2, par.Model.4, var.Model.4)

se.vc.Model.4.td <- data.frame(
  Names = c(
    "Tau.intercept.study",
    "Tau.level_AB.study",
    "Cov((intercept),level_AB).study",
    "Tau.intercept.cluster",
    "Tau.level_AB.cluster",
    "Cov((intercept),level_AB).cluster",
    "Tau.intercept.case",
    "Tau.level_AB.case",
    "Cov((intercept),level_AB).case",
    "CorStruct",
    "Sigma.sq(Intervention)",
    "Sigma.sq(Maintenance)",
    "Sigma.sq(Baseline)"
  ),
  Values = round(se.vc.Model.4, digits = 5)
)
rownames(se.vc.Model.4.td) <- NULL
colnames(se.vc.Model.4.td) <-
  c("Parameter Names", "Standard Errors")
print(se.vc.Model.4.td, row.names = FALSE)
```

#### **Autocorrelation**

```{r, fig.align = 'center', fig.width = 7, fig.height = 4}
acf_Model.4 <- ACF(Model.4, maxLag = 14) 
acf_Model.4.plot <- plot(acf_Model.4, alpha = .05)
acf_Model.4.value <- tidy(acf_Model.4$ACF) %>%
  mutate(acf = round(x, 2)) %>%
  select(acf)
acf_Model.4.tb <-
  tableGrob(acf_Model.4.value[1:10,],
            rows = NULL,
            theme = ttheme_default(base_size = 10))
grid.arrange(acf_Model.4.plot,
             acf_Model.4.tb,
             nrow = 1,
             widths = c(0.85, 0.15))
```

# Supplemental Materials 

![](data/Supplemental Materials (SCD analysis).pdf){width=100% height=700}
